Two NIRCam Arms are Better than One: How JWST Can Do More Science with NIRCam's Short-Wavelength Dispersed Hartmann Sensor

### 2016-08-05 ms.tex
Jarron rearranged the figures to make them better aligned with the text.

%Packages
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}

@@

The James Webb Space Telescope (JWST) \citep[e.g.][]{gardner2006SSRv} has the potential to profoundly expand and deepen the science of transiting exoplanets \citep[e.g.][]{greene2016jwst_trans}.
The wavelength coverage from 0.6$\mu$m to 28$\mu$m adds significantly to the wavelengths covered by the Hubble Space Telescope (HST) (currently 0.09$\mu$m to 1.7$\mu$m).
Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent observatory for characterizing the atmospheres of planets that transit their host stars with time series observations.
Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to it host star.
Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes.

No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
The largest bandwidths possible are NIRSpec's low resolution prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m.
Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7 $\mu$m to 12 $\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7 to 2.5$\mu$m), two with NIRCam's long-wavelength arm (2.44$\mu$m to 4.98 $\mu$m) \footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours.
This was calculated with the Astronomer's Proposal Tools software\footnote{http://www.stsci.edu/hst/proposing/apt} with the NIRISS SOSS mode, NIRCam's F322W2 and F444W grism time series and the MIRI Low Resolution spectrograph (LRS).

@@

The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5 $\mu$m.
This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength arm and long-wavelength arm, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0 to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{molecules_DHS_HD209.pdf}
\caption{Model spectra separated by molecule for HD 209458b.
The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm.
The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:209spec}
\end{figure}

@@

@@

\begin{figure}[!ht]
\includegraphics[width=0.5\textwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:saturationLim}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time. A planet metallicity of 22 $\times$ solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
Similar wavelength coverage can be achieved in just 3 different transits or $\sim$ 33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
\end{figure}

We use CHIMERA and a Markov Chain Monte Carlo (MCMC) retrieval to recover the individual atmospheric abundances of the simulated spectrum.
The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile 2) the altitude of the 10-bar pressure surface where the model begins 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths 4) through 11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively 12) an amplitude of a Raleigh-like haze and 13) a power law index for the Raleigh-type haze.
We assume flat priors in log space for all abundances from volume mixing ratios of 10$^{-12}$ to 1.
The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 to allow for burn-in.

@@

The posterior distributions for retrieved parameters for the most important abundances are shown in Figures \ref{fig:corner209} and \ref{fig:cornerHATp12}.
We show the posterior distributions for two cases:
\begin{enumerate}
\item \label{it:DHSgr} An observation with the long wavelength grisms alone (2.4$\mu$m to 5.0$\mu$m), shown in green.
\item \label{it:grAlone} An observation with the long wavelength grisms (2.44$\mu$m to 5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue
\end{enumerate}
For the spectral data they have in common (2.4$\mu$m to 5.0$\mu$m), we use the same noise instance to make direct comparison easier.

The posterior distributions for HD 209458b in Figure \ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used with the long wavelength grisms (Case \ref{it:DHSgr}) as compared to the long wavelength grisms alone (Case \ref{it:grAlone}).
These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (green).
The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range. Abundances are given in Log$_{10}$(ppm). Cloud pressure is in Log$_{10}$(bar).}\label{fig:corner209}
\end{figure*}

@@

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
\caption{Posterior distributions an MCMC retrieval of parameters for HAT-P-12b with the DHS (blue) and without the DHS (gray).}\label{fig:cornerHATp12}
\end{figure*}

@@

@@

\subsection{DHS properties}
The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength arm and long wavelength arm.
The maximum wavelength range for the F150W2 filter in the short wavelength arm is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
Figure \ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
There will be about a \DHSgap$\mu$m gap in the spectrum due to the gap between short wavelength detectors.
The center of this gap depends on source position.
The DHS can be used in tandem with either the F322W2 or F444W filter for the long wavelength grism observations.
The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
If the region from 2-2.23 $\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength arms.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.4\textwidth]{dhs_res.pdf}
\caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
\end{figure}

\begin{table}
\centering
\begin{tabular}{ccr}
		& DHS	& Grism \\
 \hline \hline		
Resolution &  \DHSres & 1200 - 1550 \\
Dispersion & 0.29 nm / px & 1.0 nm / px \\
Wavelengths & 1.05 - 2.00$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
			 & 1.75 - 2.23$\mu$m (F200W)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
			& 	1.01 - 1.94$\mu$m (F150W2) \footnote{For a field point matched to the F444W filter and long wavelength grism. There is a \DHSgap$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
Plate Scale & 32 mas/px  &  65 mas / px\\
Undeviated \\Wavelength & 1.36 $\mu$m & 3.94 $\mu$m   \\
\hline
\end{tabular}
\caption{Properties of DHS and simultaneous long-wavelength grism spectra. The parameters are for the A-side grism in the direction aligned with detector rows (R).}\label{tab:DHSgprop}
\vspace{0.1in}
\end{table}

@@

A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength arm and one spectrum on the long-wavelength arm -- see Figure \ref{fig:DHSwaveWGrism}.
The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
We elected to clock the pupil wheel by 1.9$^\circ$ in order to align the spectra with rows on the short wavelength detector.
Aligning spectra along the rows enables small stripe mode readouts (such as 2048 $\times$ 64) to read one DHS spectra simultaneously with long wavelength grism spectra.
This is needed for bright targets that will saturate the long wavelength detector with longer frame times, as discussed in Section \ref{sec:readout}.
There is a price for clocking the DHS pupil wheel to align spectra with rows: all DHS grisms are partially obscured by either the secondary supports or the outer edges of the primary, save element 7.
Fortunately, the relative obscuration for all 10 DHS spectra is small, going from 32\% total throughput when the pupil wheel is centered (which produces tilted spectra), versus 29\% if the pupil wheel is clocked to align the spectra along rows.
Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum where 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure \ref{fig:DHSvsPupilOverlay}.

\begin{figure}
\centering
\includegraphics[width=0.49\textwidth]{grism_pos_for_max_wcoverage.pdf}
\caption{DHS Wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source. The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes. The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
\end{figure}

@@

\begin{table}
\centering
\begin{tabular}{cc}
DHS \# & Pupil Fraction \\
\hline \hline
1 & 0.012 \\
2 & 0.032 \\
3 &  0.032 \\
4 & 0.040 \\
5 & 0.021 \\
6 & 0.015 \\
7 & 0.042 \\
8 & 0.040 \\
9 & 0.036 \\
10 & 0.022 \\
\hline
Total & 0.292
\end{tabular}
\caption{Pupil Coverage}\label{tab:pupfrac}
\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}
\end{table}

\begin{figure}
\centering
\includegraphics[width=0.49\textwidth]{dhs_pupil_labels_modA.pdf}
\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}. 
The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
The pupil wheel is clocked to make the DHS spectra straight along rows.
This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.49\textwidth]{readout_schematic.pdf}
\caption{Schematic of example readout modes for an exposure that is 12 frame times in duration.
A single FITS file is saved for the exposure, consisting of 1 or more groups per integration.
No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but will saturate more easily.}\label{fig:readout}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=0.49\textwidth]{example_ap_sizes.pdf}
\caption{Example DHS image on the A1 short wavelength detector taken during cryogenic vacuum testing of the flight hardware -- see Figure \ref{fig:DHSwaveWGrism} for the detector's position.
Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay} and pupil fraction in Table \ref{tab:pupfrac}.
The sub-array size options currently available (all 2048 pixels wide) are shown with selections for the brightest spectra available - elements 7 and 8.}\label{fig:DHSaps}
\end{figure}

@@

\section{Acknowledgements}

@@

\acknowledgments

>>>>

%Packages
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}
\usepackage{graphicx}
%\usepackage{caption}
\usepackage{subcaption}

@@

The James Webb Space Telescope \citep[JWST; e.g.][]{gardner2006SSRv} has the potential to profoundly expand and deepen the science of transiting exoplanets \citep[e.g.][]{greene2016jwst_trans}.
The wavelength coverage from 0.6$\mu$m to 28$\mu$m adds significantly to the wavelengths covered by the Hubble Space Telescope (HST) (currently 0.09$\mu$m to 1.7$\mu$m).
Its unprecedented infrared sensitivity and stable orbit at the second Lagrange (L2) point make it an excellent observatory for characterizing the atmospheres of planets that transit their host stars with time series observations.
Ground-based observatories and the Hubble Space Telescope have made important measurements of Na, K, H$_2$O in a variety of hot Jupiter, hot Neptune planets \cite[e.g.][]{snellen2008Na209,kreidberg2014wasp43,fraine2014hatp11,deming13,sing2016continuum}.
JWST has the capability of characterizing carbon-bearing molecules such as CH$_4$, CO and CO$_2$ to improve measurements of planet metallicity and C/O in comparison to it host star.
Depending on the composition and size of the clouds and hazes in exoplanet atmospheres, the longer wavelengths observed by JWST may penetrate these clouds and hazes.

No single JWST instrument may measure a spectrum over the full wavelength range from 0.6$\mu$m to 28$\mu$m, so multiple transits or secondary eclipses are necessary to piece together a broadband spectrum.
The largest bandwidths possible are NIRSpec's low resolution prism covering 0.7$\mu$m to 5$\mu$m and MIRI's low resolution prism (LRS) covering 5$\mu$m to 12$\mu$m.
Unfortunately, NIRSpec's low resolution prism mode is so sensitive, it saturates for most sources at a $J$ magnitude of $\sim$11 \citep{beichman2014pasp}, so many nearby bright planet systems must be observed with higher resolution (but smaller wavelength coverage) modes and instruments.
For example, to create a transmission spectrum for HD 209458b \citep{henry00,charbonneau00} from 0.7$\mu$m to 12$\mu$m, an observer would have to stitch together at least four different transits: one with NIRISS (0.7$\mu$m to 2.5$\mu$m), two with NIRCam's long-wavelength arm (2.44$\mu$m to 4.98$\mu$m)\footnote{Or, alternatively NIRSpec's G235H and G395H  grisms covering 1.7~$\mu$ to 5.0$\mu$m.} and one with MIRI (5$\mu$m to 12$\mu$m).
With typical overheads of $\sim$2 hr for 9 hours of pre-ingress, transit and post-ingress, this totals to about ~11 hours per transit or 44 JWST hours.
This was calculated with the Astronomer's Proposal Tools software\footnote{http://www.stsci.edu/hst/proposing/apt} with the NIRISS SOSS mode, NIRCam's F322W2 and F444W grism time series and the MIRI Low Resolution spectrograph (LRS).

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{molecules_DHS_HD209.pdf}
\caption{Model spectra separated by molecule for HD 209458b.
The new DHS mode would allow simultaneous spectra at 1-2$\mu$m ``for free'' when observing with either NIRCam's F322W2 or F444W slitless grism observations in its long-wavelength arm.
The simulated data are for one transit in each of the long-wavelength grism modes, each accompanied by simultaneous DHS grism spectra.
The observations longer than 5$\mu$m are simulated for MIRI's Low Resolution Spectrometer.}\label{fig:209spec}
\end{figure}

The NIRCam instrument can reduce the number of transits needed to build up a transmission or emission spectrum of a planet from 1$\mu$m to 5$\mu$m.
This is because the instrument has a dichroic that splits the incoming beam into a short-wavelength arm and long-wavelength arm, so simultaneous imaging and/or spectroscopy are possible at short ($<$2.4$\mu$m) and long ($>$2.4$\mu$m) wavelengths.
In particular, the DHS can be used to simultaneously cover 1.0$\mu$m to 2.0$\mu$m while the long-wavelength grisms cover either 2.44$\mu$m to 4.02$\mu$m (with the F322W2 filter) or 3.88$\mu$m to 4.98$\mu$m (with the F444W) filter.
Thus, the DHS data comes ``for free'' with any long-wavelength NIRCam grism data, aside from readout and data rate considerations discussed in Section \ref{sec:readout}.
For the example above of HD 209458b, this could save about 11 JWST hours per transit if the wavelengths from 2.0$\mu$m to 2.4$\mu$m and higher Signal to Noise ratios (SNRs) from NIRISS are not required.
The DHS is expected to perform similarly to HST's WFC3 grisms, so it is like a free coordinated HST observation for every long-wavelength NIRCam grism transit.

@@

\begin{figure}[!b]
\includegraphics[width=1.0\columnwidth]{sat_limits.jpg}
\caption{Saturation limits of the DHS mode (blue), and long-wavelength grism's F322W2 filter (red) and F444W filter (light green) for a G2V star.
The magnitudes are Vega K magnitudes where 80\% of the well depth is filled in the standard CDS readout mode described in Figure \ref{fig:readout}  for a 2048 $\times$ 64 pixel sub-array using 4 amplifiers.
The filters used are F150W2 (blue), F322W2 (red) and F444W (green).}\label{fig:saturationLim}
\end{figure}

@@

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{HAT-P-12b_kmr_cloudy_dhs.pdf}
\caption{Model spectra separated by molecule for for the inflated warm Saturn HAT-P-12b, with an opaque cloud deck at 1 mbar.
Error bars shown are for simulated observation with the DHS grism, F322W2 and F444W modes, for a total of 2 transits or about 17 hours of JWST time. A planet metallicity of 22~$\times$~solar was assumed from the relation in \citet{kreidberg2014wasp43}.}\label{fig:HATp12spec}
\end{figure}

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{HD209458b_solar_clear_1transit_DHS_vs_NIRISS_NIRCam_MIRILRS_R100.pdf}
\caption{Calculated SNR for one transit of the hot Jupiter HD209458b for the NIRISS SOSS mode, NIRCam F322W2 and F444W filters and the MIRI LRS mode for a total of 4 different transits or $\sim$44 JWST hours.
Similar wavelength coverage can be achieved in just 3 different transits or $\sim$33 hours if the DHS mode is enabled (bottom spectrum).}\label{fig:DHSvsNIRISS209}
\end{figure}

\begin{figure*}[t]
\centering
\begin{subfigure}{0.48\textwidth}
	\includegraphics[width=1\textwidth]{HD209458b_solar_clear_1trans_corner.png}
	\caption{HD209458b}
	\label{fig:corner209}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
	\includegraphics[width=1\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
	\caption{HAT-P-12b}
	\label{fig:cornerHATp12}
\end{subfigure}
	\caption{Posterior distributions for MCMC runs of HD209458b and HAT-P-12b with the DHS (blue) and without the DHS (green). The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range. Abundances are given in $\log_{10}$~(ppm). Cloud pressure is in $\log_{10}$~(bar).}
	\label{fig:corner}
\end{figure*}

We use CHIMERA and a Markov Chain Monte Carlo (MCMC) retrieval to recover the individual atmospheric abundances of the simulated spectrum.
The retrieval model includes 13 free parameters: 1) the temperature of the isothermal profile; 2) the altitude of the 10-bar pressure surface where the model begins; 3) a cloud pressure level below which all stellar flux is absorbed at all wavelengths; 4) through 11) the abundances of H$_2$O, CH$_4$, CO, CO$_2$, NH$_3$, C$_2$H$_2$, HCN, N$_2$, respectively; 12) an amplitude of a Raleigh-like haze; and 13) a power law index for the Raleigh-type haze.
We assume flat priors in log space for all abundances from volume mixing ratios of 10$^{-12}$ to 1.
The autocorrelation time for the retrievals is about ~100 steps and we run all retrievals to 20,000 steps, only using the last 5,000 to allow for burn-in.

@@

The posterior distributions for retrieved parameters for the most important abundances are shown in Figure~\ref{fig:corner}.
We show the posterior distributions for two cases:
\begin{enumerate}
\item \label{it:DHSgr} An observation with the long wavelength grisms alone (2.4-5.0$\mu$m), shown in green.
\item \label{it:grAlone} An observation with the long wavelength grisms (2.4-5.0$\mu$m) with simultaneous DHS spectra (1.0-2.0$\mu$m), shown in blue.
\end{enumerate}
For the spectral data they have in common (2.4$\mu$m to 5.0$\mu$m), we use the same noise instance to make direct comparison easier.

The posterior distributions for HD 209458b in Figure~\ref{fig:corner209} show improved constraints on the temperature, cloud pressure level and the abundances of H$_2$O, CO and CO$_2$ when the DHS is used with the long wavelength grisms (Case~\ref{it:DHSgr}) as compared to the long wavelength grisms alone (Case~\ref{it:grAlone}).
These improvements come about, in part, because the 1.0$\mu$m to 2.0$\mu$m wavelength region probes to deeper pressure layers ($\sim$ 400 mbar) to exclude clouds and better constrain the scale height.

%\begin{figure*}
%\centering
%\includegraphics[width=1.0\textwidth]{HD209458b_solar_clear_1trans_corner.png}
%\caption{Posterior distributions an MCMC run of HD209458b with the DHS (blue) and without the DHS (green).
%The H$_2$O correlates strongly with CO$_2$ and CO, meaning that improved measurements of H$_2$O with the DHS actually help improve constraints on the Carbon bearing species, even though there aren't any significant CO or CO$_2$ features in the 1-2$\mu$m range. Abundances are given in Log$_{10}$(ppm). Cloud pressure is in Log$_{10}$(bar).}\label{fig:corner209}
%\end{figure*}

@@

%\begin{figure*}
%\centering
%\includegraphics[width=1.0\textwidth]{HAT-P-12b_kmr_cloudy_corner.png}
%\caption{Posterior distributions an MCMC retrieval of parameters for HAT-P-12b with the DHS (blue) and without the DHS (gray).}\label{fig:cornerHATp12}
%\end{figure*}

@@

\begin{table*}[!t]
\centering
\begin{tabular}{lcc}
\hline \hline
 & DHS & Grism \\
\hline \hline		
Resolution: &  \DHSres & 1200 - 1550 \\
Dispersion: & 0.29 nm / px & 1.0 nm / px \\
Wavelengths: & 1.05 - 2.00$\mu$m (F150W2)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
			 & 1.75 - 2.23$\mu$m (F200W)\footnote{For a field point matched to the F322W2 filter and long wavelength grism.} & 2.44 - 4.02$\mu$m (F322W2)\\
			& 	1.01 - 1.94$\mu$m (F150W2) \footnote{For a field point matched to the F444W filter and long wavelength grism. There is a \DHSgap$\mu$m gap between detectors that depends on field position.}		& 3.88 - 4.98$\mu$m (F444W) \\
Plate Scale: & 32 mas / px  &  65 mas / px\\
Undeviated Wavelength: & 1.36$\mu$m & 3.94$\mu$m   \\
\hline
\end{tabular}
\caption{Properties of DHS and simultaneous long-wavelength grism spectra. The parameters are for the A-side grism in the direction aligned with detector rows (R).}\label{tab:DHSgprop}
\vspace{0.1in}
\end{table*}

@@

\subsection{DHS properties}
The DHS expands the wavelength range that NIRCam can achieve on a single observation by simultaneously obtaining spectroscopy with NIRCam's short wavelength arm and long wavelength arm.
The maximum wavelength range for the F150W2 filter in the short wavelength arm is fixed at 1.01 to 2.02$\mu$m with the region from 2.02-2.35$\mu$m contaminated by second order overlap.
The DHS are slitless, so the resolution is set by the pupil sizes of the individual DHS elements, which are approximately the same width in the dispersion direction.
Figure \ref{fig:DHSRes} shows the resolution as a function of wavelength, estimated from a narrowly peaked input spectrum and the fits to the spatial width along the spectrum.
There will be about a \DHSgap$\mu$m gap in the spectrum due to the gap between short wavelength detectors.
The center of this gap depends on source position.
The DHS can be used in tandem with either the F322W2 or F444W filter for the long wavelength grism observations.
The properties of the DHS, which can be used simultaneously with the long-wavelength grisms, are listed in Table \ref{tab:DHSgprop}.
If the region from 2-2.23$\mu$m is highly desirable such as for measuring the CH$_4$ feature shown in Figure \ref{fig:HATp12spec}, the DHS can be used with a F200W filter (1.75 to 2.23$\mu$m half maximum) to partially fill in the gap between the short to long wavelength arms.

\begin{figure}[!ht]
\centering
\includegraphics[width=1.0\columnwidth]{dhs_res.pdf}
\caption{Resolution as a function of wavelength for the DHS.}\label{fig:DHSRes}
\end{figure}

@@

\begin{figure}[b]
\centering
\includegraphics[width=1.0\columnwidth]{dhs_pupil_labels_modA.pdf}
\caption{DHS pupil coverage by each of the 10 DHS prisms, with the fractional throughput given in Table \ref{tab:pupfrac}. 
The throughput is modulated by the size of the DHS grism as well as whether it coincides with a secondary mirror support (inverted "Y" shaped feature).
The pupil wheel is clocked to make the DHS spectra straight along rows.
This moves the DHS elements off-center from JWST's pupil and thus decreases the throughput for elements 1 and 6, but the overall combined throughput for all 10 elements is only reduced from 32\% to 29\%.}\label{fig:DHSvsPupilOverlay}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{grism_pos_for_max_wcoverage.pdf}
\caption{DHS wavelength coverage for two field positions that will permit grism spectroscopy simultaneously with the F322W2 and F444W filters in the long wavelength arm for the same input source. The V2/V3 axes show the JWST observatory axes and the detectors (A1 - A5) are shown with their (0,0) corners as black boxes. The circles plotted for each grism are the shortest usable wavelength, undispersed wavelength and longest usable wavelength.}\label{fig:DHSwaveWGrism}
\end{figure*}

A point source observed with the DHS and grism modes of NIRCam will produce 10 spectra on the short-wavelength arm and one spectrum on the long-wavelength arm -- see Figure \ref{fig:DHSwaveWGrism}.
The DHS spectra span two of NIRCam's short-wavelength detectors covering $\sim$1 to $\sim$ 2$\mu$m with a \DHSgap$\mu$m gap due to the separation between detectors.
The DHS mode is well suited for one bright source because it spreads the light over the 10 separate spectra, but is ill-suited for a crowded field, where the spectra would overlap.
Each of the DHS spectra are separated in the spatial direction by an average of 123 pixels, so a sub-array of at least 1300 pixels must be extracted to gather all DHS flux for a single source.
Each DHS spectrum roughly covers 4\% of the JWST pupil, though they vary in size and throughput depending on where they lie relative to the secondary mirror strut supports, seen in Figure \ref{fig:DHSvsPupilOverlay}.
We elected to clock the pupil wheel by 1.9$^\circ$ in order to align the spectra with rows on the short wavelength detector.
Aligning spectra along the rows enables small stripe mode readouts (such as 2048 $\times$ 64) to read one DHS spectra simultaneously with long wavelength grism spectra.
This is needed for bright targets that will saturate the long wavelength detector with longer frame times, as discussed in Section \ref{sec:readout}.
There is a price for clocking the DHS pupil wheel to align spectra with rows: all DHS grisms are partially obscured by either the secondary supports or the outer edges of the primary, save element 7.
Fortunately, the relative obscuration for all 10 DHS spectra is small, going from 32\% total throughput when the pupil wheel is centered (which produces tilted spectra), versus 29\% if the pupil wheel is clocked to align the spectra along rows.
Table \ref{tab:pupfrac} lists the fractional pupil coverage of each DHS spectrum where 1.00 would use the entire pupil and thus take advantage of the maximum JWST collecting area.
For a sub-array size encompassing only 1 DHS spectrum (such as a 2048 $\times$ 64 subarray), the largest unobscured DHS grisms should be used - element number 7 in Figure~\ref{fig:DHSvsPupilOverlay}.

\begin{table}[!ht]
\centering
\begin{tabular}{cc}
\hline \hline
DHS \# & Pupil Fraction \\
\hline \hline
1  & 0.012 \\
2  & 0.032 \\
3  & 0.032 \\
4  & 0.040 \\
5  & 0.021 \\
6  & 0.015 \\
7  & 0.042 \\
8  & 0.040 \\
9  & 0.036 \\
10 & 0.022 \\
\hline
Total & 0.292\\
\hline
\end{tabular}
\caption{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area}
\label{tab:pupfrac}
%\tablecomments{The approximate pupil coverage of the 10 DHS grisms compared to the total primary collecting area.}
\end{table}

@@

@@

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{readout_schematic.pdf}
\caption{Schematic of example readout modes for an exposure that is 12 frame times in duration.
A single FITS file is saved for the exposure, consisting of 1 or more groups per integration.
No reset frames or dropped frames are saved.``1 Group Readout" can be used to increase the saturation limits provided that drifts between reset levels are sufficiently stable.
The BRIGHT1 readout increases the observing efficiency and reduces data volume over CDS but will saturate more easily.}\label{fig:readout}
\end{figure}

@@

\begin{figure}[!t]
\includegraphics[width=1.0\columnwidth]{example_ap_sizes.pdf}
\caption{Example DHS image on the A1 short wavelength detector taken during cryogenic vacuum testing of the flight hardware -- see Figure \ref{fig:DHSwaveWGrism} for the detector's position.
Each element is labeled corresponding to the DHS apertures shown in Figure \ref{fig:DHSvsPupilOverlay} and pupil fraction in Table \ref{tab:pupfrac}.
The sub-array size options currently available (all 2048 pixels wide) are shown with selections for the brightest spectra available - elements 7 and 8.}\label{fig:DHSaps}
\end{figure}

@@

\section*{Acknowledgements}
%\acknowledgments

@@

%\acknowledgments
